Mahotas: Open source software for scriptable computer vision

### 2013-04-23 paper.tex
REF Add some missing references

\begin{description}
\item[\textsc{Surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This
includes both keypoint detection and descriptor computation.
\item[Features] Global feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, and threshold adjacency
statistics (both the original~\citep{Hamilton2007} and the parameter-free
versions~\citep{Coelho2010}).
\item[Wavelet] Haar and Daubechies wavelets. Forward and inverse transforms are
supported.
\item[Morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[Watershed] seeded watershed and distance map
transforms~\citep{felzenszwalb}.
\item[Filtering] Gaussian filtering, edge finding, and general convolutions.
\item[Polygon operations] convex hull, polygon drawing.
\end{description}

>>>>

\begin{description}
\item[\textsc{Surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This
includes both keypoint detection and descriptor computation.
\item[Features] Global feature descriptors. In particular, Haralick texture
features~\citep{Haralick1973}, Zernike moments, local binary
patterns~\citep{Ojala2002}, and threshold adjacency statistics (both the
original~\citep{Hamilton2007} and the parameter-free
versions~\citep{Coelho2010}).
\item[Wavelet] Haar and Daubechies wavelets~\citep{Daubechies90}. Forward and
inverse transforms are supported.
\item[Morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[Watershed] seeded watershed and distance map
transforms~\citep{felzenszwalb}.
\item[Filtering] Gaussian filtering, edge finding, and general convolutions.
\item[Polygon operations] convex hull, polygon drawing.
\end{description}
